Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-11 paper/main.tex
Cython discussion

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% Describe inconsistencies in the numbers, and try to explain them.
% Time spent not hashing varies because: Variable use of CPU regs?
%
% Compare our results with general (SUPERCOP) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
% Mention that some SUPERCOP candidates are missing UPDATE-functionality.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?
% Time gain of removing ``double'' SHA-256. Double only in digest().
%
% Implications of only testing immutable files? (mutable files also
%   include directories)
% Adding a capability to support new hash functions in tahoe. (Our
%   current way breaks backwards compability)
%
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
%
% More general stuff. What could have been done differently? Criticize
% ourselves.

>>>>

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% Describe inconsistencies in the numbers, and try to explain them.
% Time spent not hashing varies because: Variable use of CPU regs?
%
% Compare our results with general (SUPERCOP) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
% Mention that some SUPERCOP candidates are missing UPDATE-functionality.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?
% Time gain of removing ``double'' SHA-256. Double only in digest().
%
% Implications of only testing immutable files? (mutable files also
%   include directories)
% Adding a capability to support new hash functions in tahoe. (Our
%   current way breaks backwards compability)
%
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
%
\section{The use of Cython}
The python-bindings generated for Cython in C are not necessarily the most
optimized versions possible to write and they are ugly to read or change (from
a C perspective). However we consider them to be good enough, and they are
equal for all the \ac{SHA}-3 candidates which means they should give the same
performance penalty. The \ac{SHA}-256 version will of course not suffer from
the same penalty, however we believe the possible performance gain is small.
This is due to the fact that no intensive operations take place in our
Cython-code.

The alternative would be creating manual Python-bindings for all the candidates
which would require a lot more work on our side, especially given the lack of a
good enough and common \ac{API} for the implementations in \ac{SUPERCOP}.
Another fact important for this decision was that we did not know exactly which
implementation of each candidate we would end up using, and we ended up trying
several for most candidates.

% More general stuff. What could have been done differently? Criticize
% ourselves.
